Back to the Future in one Week — Implementing a Smalltalk VM in PyPy

### 2014-09-19 talk/s3-2008/talk.tex
tweak

\frame[containsverbatim, plain, shrink=10]{
  \begin{verbatim}
bool_ops = [
    (LESSTHAN, operator.lt),
    (GREATERTHAN, operator.gt),
    (LESSOREQUAL, operator.le),
    (GREATEROREQUAL,operator.ge),
    (EQUAL, operator.eq),
    (NOTEQUAL, operator.ne)
    ]

>>>>

\frame[containsverbatim, plain, shrink=10]{
  \begin{verbatim}
bool_ops = [
    (LESSTHAN, lambda x, y: x < y),
    (GREATERTHAN, lambda x, y: x > y),
    (LESSOREQUAL, lambda x, y: x <= y),
    (GREATEROREQUAL,lambda x, y: x >= y),
    (EQUAL, lambda x, y: x == y),
    (NOTEQUAL, lambda x, y: x != y)
    ]
